A Large-Scale Study of the Use of Eval in R

### 2020-08-26 inst/paper/main.tex
Fix infrastructure

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{url}

@@

\newcommand{\eval}{\texttt{eval}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}

@@

This section describes the infrastructure we used to run the dynamic program
analysis to record the calls to evals.

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{listings}
\usepackage{hyperref}
\newcommand{\missingNumber}{\textcolor{red}{XX}\xspace}
\newcommand{\missingPercentage}{\textcolor{red}{XX\%}\xspace}
\newcommand{\missingTable}{\textcolor{red}{XXTable}\xspace}
\newcommand{\missingGraph}{\textcolor{red}{XXGraph}\xspace}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{paralist}
\usepackage{xspace}
\usepackage{url}

@@

\newcommand{\eval}{\texttt{eval}\xspace}
\renewcommand{\c}[1]{\lstinline{#1}\xspace}
\newcommand{\miss}[1]{{\textcolor{red}{#1}}\xspace}
\newcommand{\evil}{\emph{evil}\xspace}
\newcommand{\instrumentr}{\emph{instrumentr}\xspace}
\newcommand{\rdyntrace}{\emph{R-dyntrace}\xspace}
\newcommand{\covr}{\emph{covr}\xspace}
\newcommand{\runr}{\emph{runr}\xspace}

@@

Our infrastructure consists of a dynamic analysis pipeline to record the calls
to evals and RMarkdown notebooks for data analysis and visualization.

Figure~\ref{fig:pipeline} shows the main steps of the pipeline. We provide the
runtime, input and output data size for each step.

@@

The pipeline begins with downloading and installing open source R packages from
CRAN for the corpus along with their dependencies. The Kaggle programs are
downloaded from \href{http://www.kaggle.com}{Kaggle} separately by a crawler.
Next, code size and coverage metrics from the installed packages are extracted
using the \href{ https://github.com/r-lib/covr}{\covr} package. This is followed
by extraction of runnable programs from R packages: tests, examples and
vignettes. The extracted programs are then run through \emph{evil} (\emph{Ev}al
\emph{I}nspection \emph{L}ibrary), a dynamic analyzer that collects information
about eval calls from program runs. This dynamic analyzer builds upon our
dynamic analysis framework, \instrumentr which is another R package that enables
us to write our dynamic analysis logic in R. It internally uses a modified R
interpreter, \rdyntrace~\cite{oopsla19a}, that exposes hooks from within the
interpreter implementation for events of interest. \instrumentr serves as an
intermediary between \rdyntrace and \evil, it intercepts the hooks exposed by
\rdyntrace and attaches R functions exported by \evil as callbacks. The \evil
callbacks execute on corresponding interpreter events. All steps of this
pipeline are parallelized. To schedule and parallelize extraction and analysis
of programs, we use our homegrown library \runr. Furthermore, \runr gracefully
handles and reports failures across large-scale program runs which greatly aids
debugging of the analysis pipeline. The data extracted by \evil from each
program is concatenated, cleaned and summarized in the post-processing phase by
custom R scripts. Finally, the summarized data is analyzed in RMarkdown
notebooks to gather insights. Apart from the figures, the data points included
in the paper are also generated by RMarkdown notebooks as latex macros.
